---
title: "library_explore"
author: "Lucius Bynum"
date: "9/21/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache=TRUE)

library(dplyr)
library(ggplot2)
library(gridExtra)
```

# Honnold Wireless Data

## Data Dictionary 

* MACID: (hashed) a unique id every network device has. 50:CC:F8:80:39:4D  is my (old) cellphone
* UUID: (hashed) a unique hashed user id
* Campus: 7C campus abbreviations, e.g. HMC
* Device Name: name given to the wireless access point: CUC-HON-1-N-CAFE
* Folder: Like Name, a hierarchical representation of the access point used in the configuration: Top > CUC > Honold Mudd Library > First Floor
* Device Location: Text description of the location: Honnold Cafe
* Connect Year: year in which a connection was initiated: 2016
* Connect Month: month in which a connection was initiated: 1
* Connect Day: day in which a connection was initiated: 3
* Connect Hour: hour in which a connection was initiated (24h): 15
* Connect Day of Week: number of the day in week in which a connection was initiated: 6
* Connect Day of Year: number of the day in year in which a connection was initiated: 3
* Total Traffic (MB): megabytes of data that passed through the connection: 23.56
* AOS: text description of the mobile device's operationg system: OS X
Manufacturer: the name of the device manufacturer: Apple

```{r, cache=TRUE}
wireless_data_path <- 'HMC\ Math\ 158/wireless/2016FallSemWireless.tsv'
ezproxy_data_path <- 'HMC\ Math\ 158/ezproxy/'

wireless <- read.delim(wireless_data_path, header = TRUE, sep = '\t')
wireless[wireless == '-'] <- NA
```

Explore.

```{r}
str(wireless)
names(wireless)
```

# EZProxy Data

Get the data.

```{r, cache=TRUE}
filelist = paste0(ezproxy_data_path, list.files(ezproxy_data_path, '*.tsv'))
is_a_ccl_file <- endsWith(filelist, 'hashed.tsv')
ccl_files <- filelist[is_a_ccl_file]
spu_files <- filelist[!is_a_ccl_file]
spu <- lapply(spu_files, function(x) read.delim(x, header = TRUE, sep = '\t'))
ccl <- lapply(ccl_files, function(x) read.delim(x, header = TRUE, sep = '\t'))
```

Concatenate the separate files, making sure column names are all aligned the same way.

```{r, cache=TRUE}
spu <- do.call(rbind, lapply(spu, function(x) x[match(names(spu[[1]]), names(x))]))
ccl <- do.call(rbind, lapply(ccl, function(x) x[match(names(ccl[[1]]), names(x))]))
```

## CCL (EZProxy Report) Data Dictionary

* hashed user id: a unique identifier for a user e.g. * f7cbed2a86c711b4e28d13f74c40acf9f2a85a61db354bd8aa22dd1f944735c8
* campus: e.g. pomona
* session start datetime: e.g. 2016-07-07 15:39:24
* session end datetime: e.g. 2016-07-07 18:57:32
* session id: a unique identifier per ezproxy session e.g. oXFj5X88FvnsWrI
* ip address: (subnet only) e.g. 66.17.192

### IP Address Subnets at Claremont

134.173.* belong to the Claremont Colleges. 

The third octet values are assigned as follows:

* 8-15      Claremont SSID Wireless
* 24-31      Claremont SSID Wireless
* 32-63      HMC
* 64-95      Pomona
* 96-103     KGI            		
* 112-123     Pitzer
* 124-127     CUC - Legacy
* 128-135     CUC
* 140-141     Keck Science     
* 144-159     Scripps
* 160-191     CMC
* 192-223     CINE Wireless
* 224-239     CGU  
* 244-245     VPN Interior (non-Administrative) 

## CCL Data

```{r}
names(ccl)
str(ccl)
```

## SPU Data Dictionary

* session: unique session id. foreign key for report
* scheme: typically the transport protocol, e.g. http
* subdomain: aka host, e.g. 'www'
* domain: often the name of the service, e.g. lexisnexis	
* tld: The final portion of a Uniform Resource Locator, e.g. 'com'	
* path: file path to the requested resource	
* query: often the requested resource, or if there's a search query it should be here	
* fragment: leftovers, e.g. preferences, tracking crap, etc.

## SPU Data

```{r}
names(spu)
str(spu)
nrow(spu)
nrow(ccl)
```

# Combined EZProxy Data
```{r, code=readLines('preprocess_ezproxy_data.R'), echo=FALSE}
```
```{r}
ccl_spu <- preprocess_ezproxy_data()
ccl2 <- preprocess_ezproxy_data_ccl()
ccl_clean <- preprocess_ezproxy_data_ccl()
levels(ccl_spu$campus) <- c('cgu', 'cmc', 'cuc', 'hmc', 'kec', 'kgi', 'pit', 'pom', 'scr', 'kec', 'pit', 'pom', 'scr')
levels(ccl2$campus) <- c('cgu', 'cmc', 'cuc', 'hmc', 'kec', 'kgi', 'pit', 'pom', 'scr', 'kec', 'pit', 'pom', 'scr')
levels(ccl_clean$campus) <- c('cgu', 'cmc', 'cuc', 'hmc', 'kec', 'kgi', 'pit', 'pom', 'scr', 'kec', 'pit', 'pom', 'scr')
```
```{r}
helper <- function(x) {
  x <- toString(x)
  if (startsWith(x, '134.173')) {
    finalPiece = strtoi(strsplit(x, '\\.')[[1]][3])
    if (finalPiece == 244 || finalPiece == 245) {
      'vpn'
    } else if ((finalPiece >= 8 && finalPiece <= 15) || (finalPiece >= 24 && finalPiece <= 31)){
      'ssid'
    } else if (finalPiece >= 32 && finalPiece <= 63) {
      'hmc'
    } else if (finalPiece >= 64 && finalPiece <= 95) {
      'pom'
    } else if (finalPiece >= 96 && finalPiece <= 103) {
      'kgi'
    } else if (finalPiece >= 112 && finalPiece <= 123) {
      'pit'
    } else if (finalPiece >= 124 && finalPiece <= 135) {
      'cuc'
    } else if (finalPiece == 140 || finalPiece == 141) {
      'keck'
    } else if (finalPiece >= 144 && finalPiece <= 159) {
      'scr'
    } else if (finalPiece >= 160 && finalPiece <= 191) {
      'cmc'
    } else if (finalPiece >= 192 && finalPiece <= 223) {
      'cine'
    } else if (finalPiece >= 224 && finalPiece <= 239) {
      'cgu'
    } else if (finalPiece >= 244 && finalPiece <= 245) {
      'vpn'
    } else {
      'on'
    }
  } else {
    'off'
  }
}

helper2 <- function(x) {
  if (x == 'off') {
    'off'
  } else if (x == 'vpn') {
    'vpn'
  } else {
    'on'
  }
}
nrow(ccl_clean)
locationCol2 <- sapply(ccl_clean$ipSubnet, helper)
locationCol <- sapply(ccl_spu$ipSubnet, helper)
ccl_spu["location"] <- as.factor(locationCol)
ccl_clean["location"] <- as.factor(locationCol2)
onOffCol <- sapply(ccl_spu$location, helper2)
onOffCol2 <- sapply(ccl_clean$location, helper2)
ccl_spu["onOff"] <- as.factor(onOffCol)
ccl_clean["onOff"] <- as.factor(onOffCol2)
nrow(ccl_spu)
ncol(ccl_spu)
```
```{r}
ccl_spu %>% select(campus, location, session) %>%  group_by(campus, location) %>% summarize(counts = n_distinct(session)) %>% ggplot(aes(x = campus, y = counts, fill = location)) + geom_bar(stat='identity') + ggtitle("Campus vs IP location") + xlab("Campus") + ylab("Count")+ theme(text=element_text(size=15), axis.text.x=element_text(angle=90, hjust=1)) 
```

```{r, fig.width=20, fig.height=16}
domainCounts <- ccl_spu %>% group_by(domain) %>% summarize(counts=n())
names(domainCounts)
domainCounts <- domainCounts %>% arrange(desc(domainCounts$counts))
domains <- domainCounts$domain[1:20]
domains
summary <- ccl_spu %>% select(campus, location, session, domain, onOff) %>% group_by(domain, onOff) %>% summarize(counts = n()) 
summary <- summary[summary$domain %in% domains,]
summary %>% ggplot(aes(x=reorder(domain, -counts), y=counts, fill=onOff)) + geom_bar(stat='identity') + ggtitle("IP location vs domain") + xlab("Domain") + ylab("Count") + theme(text=element_text(size=40), axis.text.x=element_text(angle=90, hjust=1)) + guides(fill=guide_legend(title="IP location"))
```

```{r, fig.width=20, fig.height=16}
domainCounts <- ccl_spu %>% group_by(domain) %>% summarize(counts=n())
names(domainCounts)
domainCounts <- domainCounts %>% arrange(desc(domainCounts$counts))
domains <- domainCounts$domain[1:20]
domains
ccl_spu_filtered <- ccl_spu[ccl_spu$onOff == 'on',]
summary <- ccl_spu_filtered %>% select(campus, location, session, domain, onOff) %>% group_by(domain, location) %>% summarize(counts = n()) 
summary <- summary[summary$domain %in% domains,]
summary %>% ggplot(aes(x=reorder(domain, -counts), y=counts, fill=location)) + geom_bar(stat='identity')  + ggtitle("IP location vs domain") + xlab("Domain") + ylab("Count") + theme(text=element_text(size=40), axis.text.x=element_text(angle=90, hjust=1)) + guides(fill=guide_legend(title="IP location"))
```
```{r}
ccl_clean <- ccl_clean[ccl_clean$session_duration_mins < 24*60, ]
ccl_clean <- ccl_clean[ccl_clean$session_duration_mins > 122, ]
ccl_clean <- na.omit(ccl_clean)
ccl2 <- ccl2[ccl2$session_duration_mins < 750,]
```
```{r}
counts <- count(ccl_clean %>% filter(campus == 'pom'), onOff)
counts
cgu <- ccl_clean %>% filter(campus == 'cgu') %>% group_by(onOff) %>% summarize(count = n()) %>% ggplot(aes(x=onOff, y=count)) + geom_bar(stat="identity") + ggtitle("CGU") + xlab("IP Location") + ylab("Count")
scr <- ccl_clean %>% filter(campus == 'scr') %>% group_by(onOff) %>% summarize(count = n()) %>% ggplot(aes(x=onOff, y=count)) + geom_bar(stat="identity") + ggtitle("SCR") + xlab("IP Location") + ylab("Count")
pom <- ccl_clean %>% filter(campus == 'pom') %>% group_by(onOff) %>% summarize(count = n()) %>% ggplot(aes(x=onOff, y=count)) + geom_bar(stat="identity") + ggtitle("POM") + xlab("IP Location") + ylab("Count")
hmc <- ccl_clean %>% filter(campus == 'hmc') %>% group_by(onOff) %>% summarize(count = n()) %>% ggplot(aes(x=onOff, y=count)) + geom_bar(stat="identity") + ggtitle("HMC") + xlab("IP Location") + ylab("Count")
cmc <- ccl_clean %>% filter(campus == 'cmc') %>% group_by(onOff) %>% summarize(count = n()) %>% ggplot(aes(x=onOff, y=count)) + geom_bar(stat="identity") + ggtitle("CMC") + xlab("IP Location") + ylab("Count")
kgi <- ccl_clean %>% filter(campus == 'kgi') %>% group_by(onOff) %>% summarize(count = n()) %>% ggplot(aes(x=onOff, y=count)) + geom_bar(stat="identity") + ggtitle("KGI") + xlab("IP Location") + ylab("Count")
pit <- ccl_clean %>% filter(campus == 'pit') %>% group_by(onOff) %>% summarize(count = n()) %>% ggplot(aes(x=onOff, y=count)) + geom_bar(stat="identity") + ggtitle("PIT") + xlab("IP Location") + ylab("Count")
grid.arrange(cgu, scr, pom, hmc, cmc, kgi, pit, ncol=3, top="Distribution of on-campus, off-campus, and vpn connections by campus")
```
```{r, fig.width=10, fig.height=8}
par(mar=c(4,6,2,2))
names(ccl_clean)
mod <- lm(session_duration_mins ~ onOff, ccl_clean)
mod2 <- lm(session_duration_mins ~ location, ccl_clean)
summary(mod)
summary(mod2)
anova(mod)
plot(ccl_clean$onOff, ccl_clean$session_duration_mins)
filtered <- ccl_clean %>% filter(location %in% c('cgu', 'cine', 'cmc', 'hmc', 'kgi', 'pit', 'pom', 'scr'))
(tci <- TukeyHSD(aov(session_duration_mins ~ onOff, ccl_clean)))
plot(tci)
mod <- lm(session_duration_mins ~ location, ccl_clean)
anova(mod)
plot(ccl_clean$location, ccl_clean$session_duration_mins, main="Session duration by IP location", xlab="IP location", ylab="Session duration (mins)")
(tci <- TukeyHSD(aov(session_duration_mins ~ location, filtered)))
plot(tci, las=1)
plot(ccl_clean$session_duration_mins, main="Session duration for 2016", ylab="Session duration (mins)")
plot(ccl2$session_duration_mins, main="Session duration for 2016", ylab="Session duration (mins)")
ggplot(data=ccl2, aes(ccl2$session_duration_mins)) + geom_histogram(bins=50) + ggtitle("Session duration") + xlab("Session duration (mins)") + ylab("Count")
```
