---
title: "library_explore"
author: "Lucius Bynum"
date: "9/21/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE, cache = TRUE)

library(dplyr)
library(readr)
library(lubridate)
library(ggplot2)
```

# Honnold Wireless Data

## Data Dictionary 

* MACID: (hashed) a unique id every network device has. 50:CC:F8:80:39:4D  is my (old) cellphone
* UUID: (hashed) a unique hashed user id
* Campus: 7C campus abbreviations, e.g. HMC
* Device Name: name given to the wireless access point: CUC-HON-1-N-CAFE
* Folder: Like Name, a hierarchical representation of the access point used in the configuration: Top > CUC > Honold Mudd Library > First Floor
* Device Location: Text description of the location: Honnold Cafe
* Connect Year: year in which a connection was initiated: 2016
* Connect Month: month in which a connection was initiated: 1
* Connect Day: day in which a connection was initiated: 3
* Connect Hour: hour in which a connection was initiated (24h): 15
* Connect Day of Week: number of the day in week in which a connection was initiated: 6
* Connect Day of Year: number of the day in year in which a connection was initiated: 3
* Total Traffic (MB): megabytes of data that passed through the connection: 23.56
* AOS: text description of the mobile device's operationg system: OS X
Manufacturer: the name of the device manufacturer: Apple

# Preprocessing

```{r, code=readLines('preprocess_wireless_data.R'), echo=FALSE}
```

```{r, cache=TRUE}
wireless <- preprocess_wireless_data()
# separate into numeric and non-numeric
numeric_data <- select_if(wireless, is.numeric)
non_numeric_data <- select_if(wireless, is.character)
summary(wireless)
```

# Group By Day

```{r}
duration_by_day <- wireless %>% 
  group_by(connect_doy) %>%
  summarize(mean_duration = mean(duration_mins))

ggplot(duration_by_day, aes(x = connect_doy, y = mean_duration)) + geom_point()

usage_by_day <- wireless %>% 
  group_by(connect_doy) %>%
  summarize(net_bytes = sum(bytesIn))

ggplot(usage_by_day, aes(x = connect_doy, y = net_bytes)) + geom_point()
```

# EZProxy Data

## CCL (EZProxy Report) Data Dictionary

* hashed user id: a unique identifier for a user e.g. * f7cbed2a86c711b4e28d13f74c40acf9f2a85a61db354bd8aa22dd1f944735c8
* campus: e.g. pomona
* session start datetime: e.g. 2016-07-07 15:39:24
* session end datetime: e.g. 2016-07-07 18:57:32
* session id: a unique identifier per ezproxy session e.g. oXFj5X88FvnsWrI
* ip address: (subnet only) e.g. 66.17.192

## SPU Data Dictionary

* session: unique session id. foreign key for report
* scheme: typically the transport protocol, e.g. http
* subdomain: aka host, e.g. 'www'
* domain: often the name of the service, e.g. lexisnexis	
* tld: The final portion of a Uniform Resource Locator, e.g. 'com'	
* path: file path to the requested resource	
* query: often the requested resource, or if there's a search query it should be here	
* fragment: leftovers, e.g. preferences, tracking crap, etc.

### IP Address Subnets at Claremont

134.173.* belong to the Claremont Colleges. 

The third octet values are assigned as follows:

* 8-15      Claremont SSID Wireless
* 24-31      Claremont SSID Wireless
* 32-63      HMC
* 64-95      Pomona
* 96-103     KGI            		
* 112-123     Pitzer
* 124-127     CUC - Legacy
* 128-135     CUC
* 140-141     Keck Science     
* 144-159     Scripps
* 160-191     CMC
* 192-223     CINE Wireless
* 224-239     CGU  
* 244-245     VPN Interior (non-Administrative) 

```{r, code=readLines('preprocess_ezproxy_data.R'), echo=FALSE}
```

```{r, cache=TRUE}
ezproxy <- preprocess_ezproxy_data()
head(ezproxy)
```


# Session by Campus

```{r}
# stacked bar by month
ezproxy %>% select(campus, session_start) %>% mutate(month = month(session_start)) %>% ggplot(aes(x = month,fill = campus)) + geom_histogram()
  
# multiple bar by month
ezproxy %>% select(campus, session_start) %>% mutate(month = month(session_start)) %>% ggplot(aes(x = month,fill = campus)) + geom_histogram(position = 'dodge')

# stats about sessions by campus
ezproxy %>% select(campus, session_duration_mins) %>% group_by(campus) %>% summarize(min_session_duration = min(session_duration_mins, na.rm = TRUE),
          mean_session_duration = mean(session_duration_mins, na.rm = TRUE),
          median_session_duration = median(session_duration_mins, na.rm = TRUE),
          max_session_duration = max(session_duration_mins, na.rm = TRUE),
          num_na_durations = sum(is.na(session_duration_mins)))
```


