---
title: "library_explore"
author: "Lucius Bynum"
date: "9/21/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)

library(dplyr)
library(readr)
```

# Honnold Wireless Data

## Data Dictionary 

* MACID: (hashed) a unique id every network device has. 50:CC:F8:80:39:4D  is my (old) cellphone
* UUID: (hashed) a unique hashed user id
* Campus: 7C campus abbreviations, e.g. HMC
* Device Name: name given to the wireless access point: CUC-HON-1-N-CAFE
* Folder: Like Name, a hierarchical representation of the access point used in the configuration: Top > CUC > Honold Mudd Library > First Floor
* Device Location: Text description of the location: Honnold Cafe
* Connect Year: year in which a connection was initiated: 2016
* Connect Month: month in which a connection was initiated: 1
* Connect Day: day in which a connection was initiated: 3
* Connect Hour: hour in which a connection was initiated (24h): 15
* Connect Day of Week: number of the day in week in which a connection was initiated: 6
* Connect Day of Year: number of the day in year in which a connection was initiated: 3
* Total Traffic (MB): megabytes of data that passed through the connection: 23.56
* AOS: text description of the mobile device's operationg system: OS X
Manufacturer: the name of the device manufacturer: Apple

# Preprocessing

```{r, code=readLines('preprocess_wireless_data.R'), echo=FALSE}
```

```{r, cache=TRUE}
wireless <- preprocess_wireless_data()
summary(wireless)
```

