---
title: "library_explore"
author: "Lucius Bynum"
date: "9/21/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(readr)
```

# Honnold Wireless Data

## Data Dictionary 

* MACID: (hashed) a unique id every network device has. 50:CC:F8:80:39:4D  is my (old) cellphone
* UUID: (hashed) a unique hashed user id
* Campus: 7C campus abbreviations, e.g. HMC
* Device Name: name given to the wireless access point: CUC-HON-1-N-CAFE
* Folder: Like Name, a hierarchical representation of the access point used in the configuration: Top > CUC > Honold Mudd Library > First Floor
* Device Location: Text description of the location: Honnold Cafe
* Connect Year: year in which a connection was initiated: 2016
* Connect Month: month in which a connection was initiated: 1
* Connect Day: day in which a connection was initiated: 3
* Connect Hour: hour in which a connection was initiated (24h): 15
* Connect Day of Week: number of the day in week in which a connection was initiated: 6
* Connect Day of Year: number of the day in year in which a connection was initiated: 3
* Total Traffic (MB): megabytes of data that passed through the connection: 23.56
* AOS: text description of the mobile device's operationg system: OS X
Manufacturer: the name of the device manufacturer: Apple

```{r, cache=TRUE}
wireless_data_path <- 'HMC\ Math\ 158/wireless/2016FallSemWireless.tsv'
ezproxy_data_path <- 'HMC\ Math\ 158/ezproxy/'

wireless <- read_delim(wireless_data_path, '\t', escape_double = FALSE, trim_ws=TRUE)
wireless[wireless == '-'] <- NA
```

Explore.

```{r}
str(wireless)
names(wireless)
summary(wireless)
wireless <- na.omit(wireless)
wireless$disconnect_month <- as.numeric(wireless$disconnect_month)
wireless$disconnect_minute <- as.numeric(wireless$disconnect_minute)
nrow(wireless)
summary(wireless)
```

Clean.
```{r}
nrow(wireless)
```

# EZProxy Data

Get the data.

```{r, cache=TRUE}
filelist = paste0(ezproxy_data_path, list.files(ezproxy_data_path, '*.tsv'))
is_a_ccl_file <- endsWith(filelist, 'hashed.tsv')
ccl_files <- filelist[is_a_ccl_file]
spu_files <- filelist[!is_a_ccl_file]
spu <- lapply(spu_files, function(x) read.delim(x, header = TRUE, sep = '\t'))
ccl <- lapply(ccl_files, function(x) read.delim(x, header = TRUE, sep = '\t'))
```

Concatenate the separate files, making sure column names are all aligned the same way.

```{r, cache=TRUE}
spu <- do.call(rbind, lapply(spu, function(x) x[match(names(spu[[1]]), names(x))]))
ccl <- do.call(rbind, lapply(ccl, function(x) x[match(names(ccl[[1]]), names(x))]))
```

## CCL (EZProxy Report) Data Dictionary

* hashed user id: a unique identifier for a user e.g. * f7cbed2a86c711b4e28d13f74c40acf9f2a85a61db354bd8aa22dd1f944735c8
* campus: e.g. pomona
* session start datetime: e.g. 2016-07-07 15:39:24
* session end datetime: e.g. 2016-07-07 18:57:32
* session id: a unique identifier per ezproxy session e.g. oXFj5X88FvnsWrI
* ip address: (subnet only) e.g. 66.17.192

### IP Address Subnets at Claremont

134.173.* belong to the Claremont Colleges. 

The third octet values are assigned as follows:

* 8-15      Claremont SSID Wireless
* 24-31      Claremont SSID Wireless
* 32-63      HMC
* 64-95      Pomona
* 96-103     KGI            		
* 112-123     Pitzer
* 124-127     CUC - Legacy
* 128-135     CUC
* 140-141     Keck Science     
* 144-159     Scripps
* 160-191     CMC
* 192-223     CINE Wireless
* 224-239     CGU  
* 244-245     VPN Interior (non-Administrative) 

## CCL Data

```{r}
names(ccl)
str(ccl)
```

## SPU Data Dictionary

* session: unique session id. foreign key for report
* scheme: typically the transport protocol, e.g. http
* subdomain: aka host, e.g. 'www'
* domain: often the name of the service, e.g. lexisnexis	
* tld: The final portion of a Uniform Resource Locator, e.g. 'com'	
* path: file path to the requested resource	
* query: often the requested resource, or if there's a search query it should be here	
* fragment: leftovers, e.g. preferences, tracking crap, etc.

## SPU Data

```{r}
names(spu)
str(spu)
```

# Combined EZProxy Data

```{r}
ccl_spu <- inner_join(spu, ccl, by = 'session')
```
